\thesistitle

### 2019-06-27 sections/research.tex
Something about 2R variability

\subsubsection{Validating the type 2R variability threshold}
In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold. This threshold,

>>>>

\subsubsection{Validating the type 2R variability threshold}
In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold. This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor. Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity. In this section we explain the way CloneRefactor uses to verify the type 2R variability threshold.
